WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-03-18 results/sec_3-observations.tex
Thesis 4.0

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the requests are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} for Scalar and Vector data with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller. The delay in inserting Grid timeseries smaller because those requests are handling asynchronously. Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms. Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ratio in \cref{se:test_plan}.

@@

\begin{table}[ht]
\caption{Throughput and Latency of load test with 30min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_30_min_summary}
\end{table}

@@

\cref{subse:obs_test_plan_all_15min} discussed about the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_30min} processed samples.
\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_15_min_summary}
\end{table}

@@

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} auto-scaling}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_auto_15_min_summary}
\end{table}

@@

\begin{table}[ht]
\caption{Throughput and Latency of Query test cases with 15min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
* → Locations & 11462 & 992 & 5 & 17569 & 1740 & 704.67 & 0.00\% & 38.3 \\ \hline
Area → Locations & 11390 & 599 & 2 & 16755 & 1047 & 514.68 & 0.00\% & 38.1 \\ \hline
Location → Parameters & 11350 & 666 & 1 & 16821 & 1179 & 632.86 & 0.00\% & 38.0 \\ \hline
Locations → Parameters & 11305 & 659 & 1 & 17459 & 1149 & 678.55 & 0.00\% & 37.8 \\ \hline
Location → Timeseries & 11269 & 647 & 2 & 32693 & 1102 & 746.51 & 0.00\% & 37.7 \\ \hline
Locations → Timeseries & 11237 & 669 & 1 & 32651 & 1162 & 889.18 & 0.00\% & 37.6 \\ \hline
Locations, Parameter → Timeseries & 11192 & 662 & 2 & 32806 & 1152 & 789.49 & 0.00\% & 37.4 \\ \hline
Area → Timeseries & 11135 & 820 & 2 & 33235 & 1461 & 877.68 & 0.00\% & 37.3 \\ \hline
Area, Parameter → Timeseries & 11084 & 864 & 1 & 16699 & 1584 & 751.00 & 0.00\% & 37.1 \\ \hline
*, Parameter → Timeseries & 11011 & 696 & 2 & 16689 & 1216 & 693.33 & 0.00\% & 36.8 \\ \hline
* → Timeseries & 10968 & 1473 & 24 & 18283 & 2467 & 912.45 & 0.00\% & 36.7 \\ \hline
\textbf{TOTAL} & 123403 & 794 & 1 & 33235 & 1536 & 789.76 & 0.00\% & 412.6 \\ \hline
\end{tabulary}
\label{tab:obs_query_15_min_summary}
\end{table}

>>>>

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the requests are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} for Scalar and Vector data with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller. The delay in inserting Grid timeseries smaller because those requests are handling asynchronously. Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms. Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ratio in \cref{se:test_plan}.

@@

\begin{table}[ht]
\caption{Throughput and Latency of load test with 30min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_30_min_summary}
\end{table}

@@

\cref{subse:obs_test_plan_all_15min} discussed about the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_30min} processed samples.
\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_15_min_summary}
\end{table}

@@

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} auto-scaling}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std.Dev. & Error & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_auto_15_min_summary}
\end{table}

@@

\begin{table}[ht]
\caption{Throughput and Latency of Query test cases with 15min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
* → Locations & 11462 & 992 & 5 & 17569 & 1740 & 704.67 & 0.00\% & 38.3 \\ \hline
Area → Locations & 11390 & 599 & 2 & 16755 & 1047 & 514.68 & 0.00\% & 38.1 \\ \hline
Location → Parameters & 11350 & 666 & 1 & 16821 & 1179 & 632.86 & 0.00\% & 38.0 \\ \hline
Locations → Parameters & 11305 & 659 & 1 & 17459 & 1149 & 678.55 & 0.00\% & 37.8 \\ \hline
Location → Timeseries & 11269 & 647 & 2 & 32693 & 1102 & 746.51 & 0.00\% & 37.7 \\ \hline
Locations → Timeseries & 11237 & 669 & 1 & 32651 & 1162 & 889.18 & 0.00\% & 37.6 \\ \hline
Locations, Parameter → Timeseries & 11192 & 662 & 2 & 32806 & 1152 & 789.49 & 0.00\% & 37.4 \\ \hline
Area → Timeseries & 11135 & 820 & 2 & 33235 & 1461 & 877.68 & 0.00\% & 37.3 \\ \hline
Area, Parameter → Timeseries & 11084 & 864 & 1 & 16699 & 1584 & 751.00 & 0.00\% & 37.1 \\ \hline
*, Parameter → Timeseries & 11011 & 696 & 2 & 16689 & 1216 & 693.33 & 0.00\% & 36.8 \\ \hline
* → Timeseries & 10968 & 1473 & 24 & 18283 & 2467 & 912.45 & 0.00\% & 36.7 \\ \hline
\textbf{TOTAL} & 123403 & 794 & 1 & 33235 & 1536 & 789.76 & 0.00\% & 412.6 \\ \hline
\end{tabulary}
\label{tab:obs_query_15_min_summary}
\end{table}
